\TitleText

### 2019-08-18 dantzig_selector/presentation_B/1_introduction.tex
First draft of presentation

\I Under mmWave setting, if the sparsity is exploited, can few observations suffice to estimate the channel?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Compressive Sensing}
{
\I The situation that the number of model parameters is much larger than the number of measurements has been well studied, and and \it{compressed sensing} (CS) address exactly that.

>>>>

\I Under mmWave setting, if the sparsity is exploited, can few observations suffice to estimate the channel?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Compressive Sensing}
{
\I The situation that the number of model parameters is much larger than the number of measurements has been well studied, and and \Emph {compressed sensing} (CS) address exactly that.

### 2019-08-18 dantzig_selector/presentation_B/3_proof.tex
First draft of presentation

\Frame {The Need of Bounding the Expected Error}
{
\I Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but it is not clear it is true for \m {\M {P}}, for what design of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}.

\I Cand\`es and Tao established the case for real matrices, but it is not clear whether complex case applies.

\I Cand\`es and Tao showed the Big-O error bound in terms of (in our notation) \m {N_H}, but it is worth investigation whether, for practical values, the algorithm converges quickly enough.
}

\Frame {Restricted Isometry Property}
{
\I \m {\V {x}} is called \m {s}-sparse, if only \m {s} of its components are nonzero.

\I We say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {x}}^2
\leq \NC \VNm {\M{\Phi} \V {x}} _2^2
\leq \RB {1+\d_s} \VNm {\V {x}} _2^2
}

\I Interpretation: \m {\M{\Phi}} is \quotation {almost unitary} up to \quotation {relative error} \m {\d_s}.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Proof Strategy}
{
\I Show that \m {\V{g}} is almost sparse

\I Find \m {\MB {E} \SB {\VNm {\M{P} \V{u}} _2 ^2}} and \m {\MB {E} \SB {\VNm {\M{P} \V{u}} _2 ^4}}

\I Bound \m {\MB {E} \SB {\VNm {\M{P} \V{u}} _2 ^k}} for \m {k=6,8,10,\dots}.

\I Bound the probability that \m {\Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2} \geq \e \VNm {\V{u}} _2 ^2} by Chernoff Bound.

\I Established that \m {\M{P}} satisfies RIP for such probability by invoking existing results

\I Substitute \m {\VNm {\V {g} _{\MC {K}}} _1} into the original Dantzig Selector Proof
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Let \m {s} be a small integer.
Call the vector of largest-magnitude \m {s^2 L} positions of \m {\V{g}} to be \m {\V{g}_A}, and remaining positions of \m {\V{g}} to be \m {\V{g}_K}, so that \m {\V{g}_A +\V{g}_K =\V{g}}

\I We can show that 
\Disp {
\NC \V{g}_K
\leq R
:= \NC \VNm {\MC {C} \SB {\M {K}^\Adj \V {a} \SB {\f}, s}} _2
\leq \m {\F{1}{3 \R{N_H}}} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Design of \m {\M{F}_B}}
{
\I Set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by \m {\l_B >0}

\I The magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
\Disp {
\NC M_{B,2}
:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^2}
=\l_R^2 \NR
\NC M_{B,4}
:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^4}
=2 \l_R^4 \NR
}

\I We have \m {\MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} =0}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Design of \m {\M{F}_R}}
{
\I Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, giving
\Disp{
\NC M_{R,2}
:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R}}^2}
=\l_R^2 \NR
\NC M_{R,4}
:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R}}^4}
=\l_R^4 \NR
}

\I We have \m {\MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2} =0}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Indicator Function}
{
\I To make expressions more compact, introduce the indication function \m {\i}, which \m {=1} only when the manner that arguments repeat agrees exactly with the subscripts

\I For example \m {\i_{2} \SB {7,7} =1}, and \m {\i_{2,2} \SB {0,3,3,0} =1}, but \m {\i_{2} \SB {5, 6} =0}

\I That is, for some injective \m {\s:\; \CB {0, \ldots, M-1} \mapsto \CB {0, \ldots, N-1}},
\Disp {
\NC \NC \i_{a_0, \ldots, a_{N-1}} \SB {x_0, \ldots, x_{M-1}} \NR
\NC =\NC \startcases
\NC 1, \MC \Q
x_0 \cdots x_{N-1}
=x_{\s \SB {0}} ^{a_0} \cdots x_{\s \SB {M-1}} ^{a_{M-1}} \NR
\NC 0, \NC \Q \Rm {otherwise} \NR
\stopcases \NR
}

}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Suffice to Ignore \m {\M{K}}}
{
\I Recall \m {\M {P} := \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}}

\I Define \m {\M{Q} :=\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R}}, then
\Disp {
\NC \V{u} ^\Adj \M{P} ^\Adj \M{P} \V{u}
= \NC \V{u} ^\Adj \M{Q} ^\Adj \M{Q} \V{u} \NR
}

\I Thus
\Disp {
\NC \VNm {\M{P} \V{u}} _2
= \NC \VNm {\M{Q} \V{u}} _2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Finding \m {\MB {E} \VNm {\M{P} \V{u}} _2 ^2}}
{
\Disp{
\NC \NC \MB{E} \SB {\VNm {\M{Q} \V{u}} _2 ^2} \NR
\NC = \NC \MB{E} \SB {
  \sum_{n_y=0}^{N_y-1}
  \Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2
} \NR
\NC = \NC
2 \sum_{n_y=0}^{N_y-1}
\sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
\MF {Re} \SB{
   \MB{E} \SB {\M{Q} \DB {n_y, n_h}^\ast}
   \MB{E} \SB {\M{Q} \DB {n_y, n_h'}}
}
\V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
\NR
\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
   \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
\NR
\NC = \NC N_y \D N_R^2 \l_B^4 \l_R^4  \D \VNm {\V{u}} _2 ^2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Confirming the RIP of \m {\M{P}}}
{
\I Finding the variance
\Disp{
\NC \Ss{Var} \SB {\VNm {\M{P} \V{u}} _2 ^2}
\leq \NC \RB {4 N_H^2 N_Y^{-3} -1} \VNm {\V{u}} _2 ^4 \NR
}

\I Using the Chebyshev Bound
\Disp{
\NC \MB{P}
\SB {
  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
  \geq \e \VNm {\V{u}} _2 ^2
}
\leq \NC \F {1} {\e^2} \RB {4 N_H^2 N_Y^{-3} -1} \NR
}
}

% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Expected Error of DS}
{
\I Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then, with \m {S =s^2 L},
\Disp {
\NC \VNm {\V {d}} _2
\leq \NC 32 s^2 L \log N_H \NR
}

\I Moreover, under the design condition
\Disp {
\NC \RB {2 N_H}^2
\approx \NC N_Y^3 \NR
}

\I The bound holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 16 \D {12}^S \d_{S}^{-S-2} \RB {N_H^2 N_Y^{-3} -\F{1}{4}} \NR
}

\I \m {\Rightarrow} Is \m {16 \D {12}^S \d_{S}^{-S-2}} unreasonably large?

\I \m {\Rightarrow} Can \m {N_H^2 N_Y^{-3} -1/4} be made small?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Technical Lemmata}
{
{\tfx
\I Define \m {\V {d} := \Hat {\V {g}} -\V {g}}

\I From optimality of \m {\Hat {\V {g}}}: \m {
\NC \VNm {\V {d} _{\MC {K}}} _1
\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {K}}} _1 \NR
}

\I From central limit theorem: \m {
\NC \MB {E} \SB {\Nm {\IP {\V {z}, \M {P} \DB {:, n_h}}}}
\leq \NC  2 \R {\log N_h} \NR
}

\I From above: \m {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC  4 \R {\log N_h} \NR
}

\I From DS paper: \m {
\NC \VNm {\V {d} _{\MC {AB}}} _2
\leq \NC \F {1}{1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}}{\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {K}}} _1 \NR
}

\I From DS paper: \m {
\NC \VNm {\V {d}} _2^2
\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{S} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
}
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Proof (1 of 2)}
{
\I By \m {\ell_p}-norm ineq., by Lemma for \m {\VNm {\M {P}^\Tr \M {P} \V {d}} _\infty},
\Disp {
\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
\leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty
\leq 4 \R {S \log N_h} \NR
}

\I By \m {\ell_p}-norm ineq., by Lemma for \m {\VNm {\V {d} _{\MC {AB}}} _2}, by above,
\Disp {
\NC \VNm {\V {d}_{\MC {A}}} _1
\leq \NC \R {S} \VNm {\V {d}_{\MC {A}}} _2 \NR
\NC \leq \NC \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
+4 \RB {1+\d_{2S}} S \R {\log N_h} \NR
}

\I By Lemma for \m {\VNm {\V {d} _{\MC {K}}} _1}, by above, by dropping terms,
\Disp {
\NC \VNm {\V {d} _{\MC {K}}} _1
\leq \NC 2 \RB {1+\d_{3S}} \VNm {\V {g} _{\MC {K}}} _1
+4 \RB {1+2\d_{3S}} S \R {\log N_h} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Proof (2 of 2)}
{
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC 16 S \log N_h
+8 \d_{3S} \R {\log N_h} 
+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {K}}} _1 \NR
\NC \leq \NC 32 s^2 L \log N_H
+\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
+\F {\pi} {9} \F {L} {s^2 N_H} \NR
\NC \leq \NC 32 s^2 L \log N_H \NR
}

1. Plug in the bound for \m {\VNm {\V {d} _{\MC {K}}} _1}

2. Plug in \m {S =s^2 L} and \m {N_h =N_H^2}
}

>>>>

\Frame {The Need of a Modified Proof}
{
\I \Emph {Q1}: Dantzig Selector works for \Emph {sparse} vectors, but while \m {\M {H}} is sparse in the angular domain, is it sparse by itself?

\I \Emph{Q2}: Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but is it true for \m {\M {P}}, and for what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}?

\I \Emph{Q3}: Cand\`es and Tao established the case for real matrices, but does \Emph {complex} case apply?

\I \Emph{Q4}: Cand\`es and Tao showed the Big-O error bound in terms of (in our notation) \m {N_H}, but does, for practical values, the algorithm converges for \Emph {high probability}?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Restricted Isometry Property}
{
\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.

\I We say that \m {\M{P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {g}}^2
\leq \NC \VNm {\M{P} \V {g}} _2^2
\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
}

\I Interpretation: \m {\M{P}} is \Emph {almost unitary} up to relative error \m {\d_s}.

\I Set shorthand, for any unit vector \m {\V{u}},
\Disp {
\NC \rho := \NC \VNm {\M{P} \V{u}}_2^2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Proof Strategy}
{
\I Show that \m {\V{g}} is almost sparse

\I Find \m {\MB {E} \SB {\rho}} and \m {\MB {E} \SB {\rho^2}}, and bound \m {\MB {E} \SB {\rho ^k}} for \m {k=3,4,5,\dots}.

\I Bound the probability that \m {\Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2} \geq \e \VNm {\V{u}} _2 ^2}.

\I Establish that \m {\M{P}} satisfies RIP for what probability

\I Take into consideration how \m {\V{g}} is not exactly sparse
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Call the vector of largest-magnitude \m {N_H L} positions of \m {\V{g}} to be \m {\V{g}_A}, and remaining positions of \m {\V{g}} to be \m {\V{g}_K}, so that \m {\V{g}_A +\V{g}_K =\V{g}}

\I We can show that 
\Disp {
\NC \V{g}_K
\leq R
:=\m {\F{1}{3 \R{N_H}}} \NR
}

\I \m {R \to 0} as \m {N_H \to \infty}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Concentration Inequality}
{

\I According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), it has been established that, if the \Emph {concentration inequality} holds that
\Disp{
\NC \MB{P}
\SB {
  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
  \geq \F {\d_s} {2} \VNm {\V{u}} _2 ^2
}
\leq \NC B \RB {\d_s, N_Y} \NR
}
\I then, supppose the probability that RIP holds for \m {\M{P}} is \m {p},
\Disp{
\NC 1 -p
\leq \NC \RB {\F {12 e N_H} {s \d_s}} ^s B \RB {\d_s, N_Y} \NR
}

\I Our task is reduced into establishment of the inequality!
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Design of Beamformers}
{
\I Considering \Emph {Q2}: If each entry of \m {\M {P}} is i.i.d., then it's likely that, by whatever variation of Central Limit Theorem,
\Disp {
\NC \MB {E} \SB {\rho ^{k}}
\approx \NC 1
\quad \Ss {in distribution} \NR
}

\I Unfortunately, they are \Emph {not i.i.d.}!
\m {\Rightarrow} Need closer scrutiny.

\I Try to set each entry of \m {\M{F}_B} (resp.\ \m {\M{W}_B}) to be i.i.d.\ Standard Complex Normal, multiplied by a design constant \m {\l_B >0} (so that the magnitude follows Rayleigh distribution).

\I And let each entry of \m {\M{F}_R} (resp.\ \m {\M{W}_B}) be uniformly distributed on the unit circle on the complex plane, multiplied by a design constant \m {\l_B >0}.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Chernoff Inequality}
{
\I Imitating the Chernoff Inequality argument in classical probability, we have, for any \m {s >0} so that, supposedly, both sides \m {< \infty},
\Disp {
\NC p
= \NC \MB{P} \SB {\rho \geq \RB {1 +\e} \MB{E} \SB {\rho}} \NR
\NC =\NC \MB{P} \SB {\Ss {e} ^{s \rho} \geq \Ss {e} ^{s \RB {1 +\e}}} \NR
\NC \leq \NC \Ss {e} ^{-s \RB {1 +\e}} \MB{E} \SB {\Ss {e} ^{s \rho}} \NR
}

\I Assuming the convergence of power series for a moment,
\Disp {
\NC \MB{E} \SB {\Ss {e} ^{s \rho}}
=\NC \sum_{k=0}^\infty \F{s ^k} {k!} \MB{E} \SB {\rho ^k} \NR
}

\I But what are the \Emph {moments} of \m {\rho}?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Finding the First Moment}
{
\I It is easy show that
\Disp {
\NC \MB{E} \SB {\rho}
= \NC N_Y^2 N_R^2 \l_B^4 \l_R^4 \D \VNm {\V{u}} _2 ^2 \NR
}

\I This motivates
\Disp {
\NC \l_B
=\NC \F {1} {\R {N_Y}},
\l_R
=\F {1} {\R {N_R}} \NR
}

\I So that
\Disp {
\NC \MB{E} \SB {\rho}
=\NC 1
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Finding the Second Moment}
{
\I We can show that, after tedius calculation,
\Disp {
\NC \MB{E} \SB {\rho ^2}
\leq \NC N_Y^4 N_R^4 \l_B^8 \l_R^8 \RB {1 +N_Y^{-2}} \D \VNm {\V{u}} _2 ^4 \NR
\NC = \NC \RB {1 +N_Y^{-2}} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Bounding Higher Moments}
{
\I We can show that, after a lot applications of various inequalities,
\Disp {
\NC \MB{E} \SB {\rho ^k}
\leq \NC N_Y^{2k} N_R^{2k} \l_B^{4k} \l_R^{4k}
\D \G \SB {k +1}^2
\D \VNm {\V{u}} _2 ^k \NR
\NC = \NC \G \SB {k +1}^2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Try to Substite the Moments of \m {\rho}...}
{
\I Plugging into the Chernoff Inequality we have
\Disp {
\NC \log p
\leq \NC \Min {s >0} \Bigg [
  -\RB {1 +\F{1}{2} \e -\F{1}{8} \e^2} s \NR
  \NC \NC \FourQ +\log \RB{
    1
    +s \MB{E} \SB {\rho}
    +\F{s ^2} {2} \MB{E} \SB {\rho^2}
    +\dots
  }
\Bigg ] \NR
}

\I We want the exponent to go small, and it looks promising.

\I But the remainder term of MGF, \m {\MB{E} \SB {\Ss {e} ^{s \rho}}}, seems to \Emph {diverge}!
\Disp {
\NC \sum_{k=3}^\infty \F{s ^k} {k!} \MB{E} \SB {\rho ^k}
\leq \NC \sum_{k=3}^\infty \F{s ^k} {k!} \G \SB {k +1}^2
= \sum_{k=3}^\infty k! \D s ^k
\to \infty \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Try Again for \m {\R {\rho}}...}
{
\I Take square roots on both sides so that \m {\sum_{k=3}^\infty s ^k} is finite for \m {s <1}.
\Disp {
\NC p
= \NC \MB{P} \SB {\rho \geq \RB {1 +\e} \MB{E} \SB {\rho}} \NR
\NC =\NC \MB{P} \SB {\Ss {e} ^{s \R {\rho}} \geq \Ss {e} ^{s \R {1 +\e}}} \NR
\NC \leq \NC \Ss {e} ^{-s \R {1 +\e}} \MB{E} \SB {\Ss {e} ^{s \R {\rho}}} \NR
}

\I The \m {1/2} and \m {3/2} moments can be bounded by Cauchy Inequality:
\Disp{
\NC \F{1}{\R{1+N_Y^{-2}}}
\leq \NC \MB{E} \SB {\R{\rho}}
\leq 1, \NR
\NC 1
\leq \NC \MB{E} \SB {\rho ^{3/2}}
\leq \R{1+N_Y^{-2}}, \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Confirming the Concentration Ineq.}
{
\I Thus, Minimizing for \m {s} we have, for any \m {\e >0},
\Disp {
\NC \NC \log p \NR
%
\NC =\NC \Min {s >0} \Bigg [
  -\RB {1 +\F{1}{2} \e -\F{1}{8} \e^2} s
  +\MB{E} \SB {\R{\rho}} s
  +\F{1}{2} \RB {\MB{E} \SB {\rho} -\MB{E} \SB {\R {\rho}}^2} s^2 \NR
  \NC \NC \FourQ +\F{1}{6} \RB {-3 \MB{E} \SB {\R {\rho}} \MB{E} \SB {\rho} +2\MB{E} \SB {\R{\rho}} ^3 +\MB{E} \SB {\rho ^{3/2}}} s^3
  +\dots
\Bigg ] \NR
%
\NC =\NC \Min {s >0} \SB{
  -\F{1}{2} \e s
  +\F{1}{2} N_Y^{-2} \RB {1 -N_Y^{-2}} s^2
  +N_Y^{-2} \RB {\F{1}{3} -\F{5}{24} N_Y^{-2}} s^3
} \NR
%
\NC =\NC -\F{\e^2 N_Y^2} {8} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Confirming the Concentration}
{
\I The lower tail can be proved in the same way as upper tail.

\I Conbining we have
\Disp{
\NC \MB{P}
\SB {
  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
  \geq \e \VNm {\V{u}} _2 ^2
}
\leq \NC 2\exp \SB {-\F{N_Y^2}{8} \e^2} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Expected Error of DS}
{
\I In answer of \Emph {Q3}, It can be checked that the generalization from real to complex does not affect the argument, but only loosen the bound by a multiple.

\I In conclusion, and also in answer of \Emph {Q4}, the bound
\Disp {
\NC \VNm {\V {d}} _2
\leq \NC 4 \R{2} \D \R{L N_H \log N_H} \NR
}

\I holds for probability \m {p}, 
\Disp {
\NC p
\geq \NC 1 -2 \D 6^{N_H L} \D \exp \SB {-\F{N_Y^2} {32}} \NR
}

\I Note that \m {p \to 1} as \m {N_Y \to \infty} exponentially.
}

### 2019-08-18 dantzig_selector/presentation_B/5_conclusion.tex
First draft of presentation

\Frame {Conclusion}
{
\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity

\I Towards that end, We adopt The Dantzig Selector (DS) rather than the popular Orthogonal Matching Pursuit (OMP)

\I We generalized DS for complex vectors, and carried it out in the angular domain

\I Analogous to original DS proof, we bound the expected square error, and the successful probability is also bounded by a constant explicit depending on system parameters \m {s} and \m{L}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Future Work}
{
\I Check the proof carefullly, especially the approximation technique

\I Finish the simulation program

\I Compare the probability bound with simulation result

\I Also implement OMP and compare they two
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {References}
{
{\tfx
\I D Achlioptas (2001). Database-friendly random projections. In Proceedings of the twentieth ACM SIGMOD-SIGACT-SIGART symposium on Principles of database systems (pp. 274-281). ACM.

>>>>

\Frame {Conclusion}
{
\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity, and studied Dantzig Selector (DS).

\I We modified DS for present setting: for almost sparsity, in the angular domain, for the almost-sparse condition, for the beamformer matrix in our setting, and for complex vectors.

\I We bound the expected square error and the successful probability, in explicit expression of system parameters such as \m {N_H}, \m {N_Y}, and \m{L}.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Future Work}
{
\I Check the proof again, especially the approximation decision.

\I Simulate many different parameters such as \m {N_H}, \m {N_Y}, and \m{L} and discuss extensively.

\I Verify (if correct) the successful-probability bound and observe how \m {N_Y, N_H} affects it (if any).

\I Also implement (some or all of) OMP, LS, LASSO among others, and compare them.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {References}
{
{\tfx
\I D Achlioptas (2001). Database-friendly random projections. In Proceedings of the twentieth ACM SIGMOD-SIGACT-SIGART symposium on Principles of database systems (pp. 274-281). ACM.
